Empowering the use of community driven preprints in ecology and evolution

### 2024-04-12 ms/ms.qmd
chaneg subtitle
Fixing up the first plot to include summary of authors. These will be on the below part of the figure

@@

# Generational gaps of preprinting in ecology and evolution

@@

p3 <- ggplot(preprints, aes(x = submitting_author_first_publication_year)) +
  geom_histogram(binwidth = 1, fill = "grey", color = "black") +
  labs(x = "Year of submitting authors first publication", y = "Number of preprints") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Get gender using all unique first names from the data set
data_genders <- data.frame(gender(unique(preprints$submitting_author_firstname)))
dim(data_genders) #514 assigned
#names(data_genders)

# Merge with main data frame
#unique(data_genders$name)
#data_genders <- rename(data_genders, submitting_author_firstname = name)
data3 <- left_join(preprints, data_genders, by = c("submitting_author_firstname"))
#names(data3)
table(is.na(data3$proportion_male)) #157 missing

# Plot the data
data4 %>% filter(!is.na(gender))  %>% ggplot2::ggplot(aes(x = gender)) + geom_bar()

@@

# Paving *our* own future of open, transparent and community driven science

>>>>

p5 <- ggplot(preprints, aes(x = submitting_author_first_publication_year)) +
  geom_histogram(binwidth = 1, fill = "grey", color = "black") +
  labs(x = "Year of submitting authors first publication", y = "Number of preprints") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Get gender using all unique first names from the data set
data_genders <- data.frame(gender(unique(data2$submitting_author_firstname)))
dim(data_genders) #514 assigned
#names(data_genders)
colnames(data_genders)[1]  <- c("submitting_author_firstname")

# Merge with main data frame
data3 <- left_join(data2, data_genders, by = c("submitting_author_firstname"))
#names(data3)
table(is.na(data3$proportion_male)) #157 missing

# Plot the data
p6 <- data4 %>% filter(!is.na(gender))  %>% tabyl(gender)  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))  %>%  ggplot(aes(x = "", y = percent, fill = gender)) +
    geom_col(color = "black") +
    geom_label_repel(aes(label = labels),
              position = position_stack(vjust = 0.6),
            show.legend = FALSE) +
    scale_fill_viridis_d() +
    coord_polar(theta = "y") + 
    theme_void() + labs(fill = "Article Type") + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")

@@

# Generational gaps in preprinting practices

@@

@@

# Paving *our* future of open, transparent and community driven science
